<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spRingsteen

<!-- badges: start -->
<!-- badges: end -->

The spRingsteen package provides a number of dataframes describing the songs,
albums, tours, and setlists of Bruce Springsteen's career. The data (collected from [Brucebase](http://brucebase.wikidot.com/)) is provided
in a tidy form which is easily analysed in `R`.

## Installation

You can install the development version of spRingsteen from GitHub like so:

``` r
remotes::install_github("obrienjoey/spRingsteen")
```

## Concerts

The package includes datasets around the career of Bruce Springsteen. For example,
the touring history of him and his numerous bands is stored in `concerts`:

```{r example}
library(spRingsteen)
library(dplyr)

concerts

# how many concerts have occurred in each country?

concerts %>% 
  count(country, sort = TRUE)
```

## Setlists

It also has information of the setlists performed in these shows which are 
stored in `setlists`.

```{r}
setlists

# what song has been played most by Springsteen?

setlists %>%
  count(song, sort = TRUE)

# which song has most frequently opened a show?

setlists %>%
  filter(song_number == 1) %>%
  count(song, sort = TRUE) %>%
  slice(1)
```

## Songs

Further details of the songs themselves are available in `songs`, including
the album of appearance and also the full lyrics in some cases. This allows for 
some text mining or sentiment analysis using a package like tidytext.

```{r}
library(tidytext)

# what word appears most frequently in the **Born in the U.S.A** album?

songs %>% 
  filter(album == "Born In The U.S.A.") %>% 
  select(title, lyrics) %>% 
  unnest_tokens(word, lyrics) %>% 
  count(word, sort = TRUE) %>% 
  anti_join(stop_words, by = 'word')
```

## Tours

Lastly, the `tour` table contains the tours associated with each concert.

```{r}
tours %>% 
  count(tour, sort = TRUE)
```

Of course the real advantage of this package is in combining the different
dataframes in order to infer useful information:

```{r}
# what was the most played song on each tour?
setlists %>% 
  left_join(tours, by = 'gig_key') %>%
  count(song, tour) %>%
  group_by(tour) %>%
  filter(n == max(n)) %>%
  arrange(desc(tour))
```
